

\addcontentsline{toc}{chapter}{References and Further Reading}


\begin{fullwidth}

\begin{thebibliography}{99}

\bibitem{averbach} B.\ Averbach and O.\ Chein. \emph{Problem Solving Through Recreational Mathematics}. Dover, 2000.

\bibitem{bag} A.K.\ Bag. \emph{Binomial Theorem in Ancient India}. Indian Journal of History of Science, vol.\ 1,  1966 68--74. 

\bibitem{baron} M.\ Baron. \emph{The Origins of the Infinitesimal Calculus}. Dover, 1987.

\bibitem{beckman} S.\ Beckmann. \emph{Mathematics for Elementary
  Teachers}. Addison Wesley, 2007.

\bibitem{bogomolny} A.\ Bogomolny. Leibniz and Pascal Triangles. \emph{Interactive Mathematics Miscellany and Puzzles}.
\\ \texttt{http://www.cut-the-knot.org/}

\bibitem{boyer} C.B.\ Boyer and U.C.\ Merzbach. \emph{A History of Mathematics}. Wiley, 1991.

\bibitem{colebrooke} H.\ Colebrooke. \emph{Classics of Indian Mathematics}. 
Sharada Publishing House, 2005.

\bibitem{dudley} U.\ Dudley. \emph{Elementary Number Theory}. Dover,
  2008.

\bibitem{dull} R.W.\ Dull. \emph{Mathematics for Engineers}. Second
  Edition. McGraw-Hill, 1941.

\bibitem{dunnMcConnell} 
E.\ Dunne and M.\ McConnell. \emph{Pianos and Continued
Fractions}. Mathematics Magazine, vol.\ 72, no.\ 2 (1999), 104-115.

\bibitem{euclid} Euclid and T.L.\ Heath. \emph{The Thirteen Books of Euclid's Elements: Volumes 1, 2, and 3}. Dover, 1956. 

\bibitem{eves} H.\ Eves. \emph{An Introduction to the History of Mathematics}. Saunders College Publishing, 1990.

\bibitem{gardner} M.\ Gardner. \emph{My Best Mathematical and Logic
  Puzzles}. Dover, 1994.

\bibitem{lange} L.J.\ Lange. \emph{An Elegant Continued Fraction for {$\pi$}}. The American Mathematical Monthly, vol. 106, no. 5, (1999), pp. 456--458.

\bibitem{livio} M.\ Livio. \emph{The Equation that Couldn't be
  Solved}. Simon\&Schuster, 2005.

\bibitem{keeneyRamaley} R.L.\ Keeney and J.F.\ Ramaley. \emph{On the Trinomial Coefficients}. Mathematics Magazine, vol. 42, no. 4 (Sep., 1969), pp. 210-213.

\bibitem{knuth} D.E.\ Knuth. \emph{The Art of Computer Programming. Volume 1: Fundamental Algorithms}. Addison-Wesley, 1975.

\bibitem{mira} J.A.\ Mira. \emph{Mathematical Teasers}. Barnes\&Noble, 1970.

\bibitem{nrich} NRICH website.
\\ \texttt{http://nrich.maths.org/}

\bibitem{papick} I.\ Papick. \emph{Algebra Connections: Mathematics
  for Middle School Teachers.} Pearson, 2007.

\bibitem{petkovic} M.\ Petkovi\'{c}. \emph{Famous Puzzles of Great Mathematicians}. American Mathematical Society, 2009.

\bibitem{polya} G.\ Polya. \emph{Mathematical Discovery: On
  Understanding, Learning, and Teaching Problem Solving.} Wiley, 1981.

\bibitem{posamentier} A.\ Posamentier. \emph{Teaching Secondary Mathematics}. Prentice-Hall, 2002.

\bibitem{tahan} M.\ Tahan. \emph{The Man Who Counted: A Collection of Mathematical Adven-
tures}. W.W.\ Norton\&Company, 1993.

\bibitem{solomon} R.\ Solomon. \emph{Abstract Algebra}. Brooks/Cole, 2003.

\bibitem{wylie} C.R.\ Wylie Jr. \emph{101 Puzzles in Thought and
  Logic}. Dover, 1957.

\bibitem{youse} B.K.\ Youse. \emph{Arithmetic: A Modern Approach}. Prentice-Hall, 1963.


\end{thebibliography}
\end{fullwidth}


%\cleardoublepage
%
\addcontentsline{toc}{chapter}{Index}
\printindex

