\newpage
\section{Shelby and Scotty}\label{A:SS}

Shelby and Scotty want to express the number $27$ in base
$4$. However, they used very different methods to do this. Let's check
them out.

\fixnote{Make the division symbols look better.}

\fixnote{Extensions in Vic's e-mail.  Bigger numbers, include a 0 in a digit.}

\fixnote{Perhaps swap the order.}

\fixnote{Convert 8630 (base ten) to base thirteen.  Quickly convert 2102 (base three) to base nine.}

\fixnote{Without using base ten, convert 341 (base six) to base four.  Without using base ten, convert 341 (base six) to base eleven.}


\begin{prob} Consider Shelby's work:
\[
4\,\begin{tabular}[b]{@{}r@{} r}
$6$ &\, R\,$\boldsymbol{3}$\\ \cline{1-1}
\Big)\begin{tabular}[t]{@{}l@{}}
$27$ 
\end{tabular}
\end{tabular}
\qquad
4\,\begin{tabular}[b]{@{}r@{} r}
$1$ &\, R\,$\boldsymbol{2}$\\ \cline{1-1}
\Big)\begin{tabular}[t]{@{}l@{}}
$6$ 
\end{tabular}
\end{tabular}
\qquad
4\,\begin{tabular}[b]{@{}r@{} r}
$0$ &\, R\,$\boldsymbol{1}$\\ \cline{1-1}
\Big)\begin{tabular}[t]{@{}l@{}}
$1$ 
\end{tabular}
\end{tabular} \qquad \Rightarrow \qquad \fbox{$123$}
\]
\begin{enumerate}
\item Describe how to perform this algorithm.
\item Provide an additional relevant and revealing example
  demonstrating that you understand the algorithm.
\end{enumerate}
\end{prob}




\begin{prob} Consider Scotty's work:
\[
4^3\,\begin{tabular}[b]{@{}r@{} r}
$0$ &\, R\,$27$\\ \cline{1-1}
\Big)\begin{tabular}[t]{@{}l@{}}
$27$ 
\end{tabular}
\end{tabular}
\qquad
4^2\,\begin{tabular}[b]{@{}r@{} r}
$\boldsymbol{1}$ &\, R\,$11$\\ \cline{1-1}
\Big)\begin{tabular}[t]{@{}l@{}}
$27$ 
\end{tabular}
\end{tabular}
\qquad
4\,\begin{tabular}[b]{@{}r@{} r}
$\boldsymbol{2}$ &\, R\,$\boldsymbol{3}$\\ \cline{1-1}
\Big)\begin{tabular}[t]{@{}l@{}}
$11$ 
\end{tabular}
\end{tabular} \qquad \Rightarrow \qquad \fbox{$123$}
\]
\begin{enumerate}
\item Describe how to perform this algorithm.
\item Provide an additional relevant and revealing example
  demonstrating that you understand the algorithm.
\end{enumerate}
\end{prob}

\begin{prob} 
Create an illustration (or series of illustrations) based on the $27$
marks below that models Shelby's method for changing bases.
\[
|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|
\]
Further, explain why Shelby's method works. 
\end{prob}

\begin{prob} 
Create an illustration (or series of illustrations) based on the $27$
marks below that models Scotty's method for changing bases.
\[
|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|\;\;|
\]
Further, explain why Scotty's method works. 
\end{prob}
