\newpage
\section{Go Climb a Tree!} 

In this activity, we'll evaluate the probabilities of complex events
using tree diagrams, fraction arithmetic, and counting.

\begin{prob}
Give a story problem that is modeled by the expression:
\[
\frac{3}{7} \times \frac{2}{5}
\]  
Let the start of the story be: ``$2/5$ of the class are girls.''  Once
you have the story, solve it using pictures (use rectangles for the
wholes) and explain why it makes sense that multiplying fractions is
the same as multiplying the numerators and multiplying the
denominators.
\end{prob}

\begin{prob}
The Weather Channel has predicted that there is a 70\% chance of rain today, a 20\% chance of rain tomorrow, and a 40\% chance of rain the day after tomorrow.  Use a tree diagram to help answer the following:
\begin{enumerate}
\item What is the probability that it will rain today and not rain tomorrow? 
\item What is the probability it will rain on exactly one of the first two days?
\item What is the probability that it will rain today, not rain tomorrow, and rain the following day?
\item What is the probability that it will rain on exactly two of the three days?
\item What is the probability it will rain on all three days?
\item What is the probability it won't rain at all?
\item What is the probability it will rain on at least one of the days?
\end{enumerate}
\end{prob}

\begin{prob}
The Indians and the Yankees are to face each other in a best-of-seven series.  The probability that the Indians will win any game is 30\%.
\begin{enumerate}
\item What is the probability that the Indians win games 1, 3, 4, and 6 to win the series?
\item What is the probability that the Indians win the series in exactly 6 games?
\item What is the probability that the Indians win the series?
\end{enumerate}
\end{prob}

\begin{prob} 
Fred the Slob has an unreliable car that starts only 65\% of the days.
If the car doesn't start, poor Fred must walk the one block to work.
This week, he is slated to work 6 days (Monday through Saturday).  
\begin{enumerate}
\item What is the probability that Fred will walk on Monday and Wednesday
and drive the other days?
\item What is the probability that Fred will
drive on exactly 4 of the days? 
\item What is the probability that poor Fred will have to walk on at least two of the days?
\end{enumerate}
\end{prob}

\begin{prob}
Use the techniques of this activity (i.e., using a special case and
fraction arithmetic to help investigate a more general case) to find
the probability of passing a 10-question multiple choice test if you
must get 70\% or more correct to pass.
\end{prob}
