\newpage
\section{The Dreaded Story Problem}\label{A:dreadedStoryProblem}

Let's try our hand at a problem involving ratios.

\begin{teachingnote}
This problem is challenging. Students must try out actually
numbers and do experiments. There are many false ``solutions'' that can be obtained.
\end{teachingnote}


\begin{prob}
On orders from his doctor, every day, Marathon Marty must run from his
house to a statue of Millard Fillmore and run back home along the same
path.  So Marty doesn't lollygag, the doctor orders him to average 8
miles per hour for the round trip or endure painful electrical shock
therapy to his big toes.  Today, Marty ran into Gabby Gilly on his way
to the statue and averaged only 6 miles per hour for the trip out to
the statue.
\begin{enumerate}
\item Name some quantities that might be associated with this problem.
Which of the quantities are constant and which can change? Which
quantities affect Marty's average rate for the round trip and what are
those effects?

\item What must Marty do to ensure he's obeyed his doctor's orders? 
Once your model is set up, solve the problem in as many ways that you
can (guess and check, algebraically, graphically, with tables, pure
reasoning, etc.).

\item Assume the doctor orders him to average 8.346 miles per hour for the round trip.
Today, Marty ran into Gabby Gilly on his way to the statue and
averaged only 6.597 miles per hour for the trip out to the statue.
What must Marty do to ensure he's obeyed his doctor's orders?
\item Now assume the doctor orders him to average 6 miles per hour for the round trip.
Being fired up, Marty ignores Gabby Gilly and averages 8 miles per
hour on the way out.  What must Marty do to ensure he's obeyed his
doctor's orders?
\item The doctor now goes back and orders Marty to average 8 miles per hour for the round trip again.
This time, Gabby Gilly tackles Marty and starts yakking at him so much
that Marty only averages 4 miles per hour on the way out.  What must
Marty do to ensure he's obeyed his doctor's orders?
\fixnote{Also try numbers near 4, such as 4.1, and 4.01.}  
\item Now the doctor orders him to average $n$ miles per hour for the round trip.
Assuming that Marty, for whatever reason, averages $m$ miles per hour on
the trip out to the statue. What must Marty do to ensure he's obeyed
his doctor's orders?
\end{enumerate}
\end{prob}

\begin{prob}
What changes can you make to this problem to make it different?
Easier? Harder?
\end{prob}
