\newpage
\section{Sieving It All Out}\label{A:Sie}
\begin{prob}  
\textit{Incognito's Hall of Shoes} is a shoe store that just
  opened in Myrtle Beach, South Carolina. At the moment, they have 100
  pairs of shoes in stock. At their grand opening 100 customers showed
  up. The first customer tried on every pair of shoes, the second
  customer tried on every 2nd pair, the third customer tried on every
  3rd pair, and so on until the 100th customer, who only tried on the
  last pair of shoes.
\begin{enumerate}
\item Which shoes were tried on by only 1 customer?
\item Which shoes were tried on by exactly 2 customers?
\item Which shoes were tried on by exactly 3 customers?
\item Which shoes were tried on by the most customers?
\item How many customers tried on the 45th pair?  
\item How many customers tried on the 81st pair?  
\end{enumerate}
In each case, explain your reasoning.
\end{prob}

\begin{prob}
Which pairs of shoes were tried on by both 
\begin{enumerate}
\item customers 3 and 5?
\item customers 6 and 8?
\item customers 12 and 30?
\item customers 7 and 13?
\end{enumerate}
\end{prob}

\begin{prob}
Which customers tried on both 
\begin{enumerate}
\item pairs 24 and 36?
\item pairs 30 and 60?
\item pairs 42 and 12?
\item pairs 28 and 15?
\end{enumerate}
\end{prob}


\newpage


\begin{prob} 
Use ideas from Incognito's Hall of Shoes to find all the primes from $1$ to $120$ \textit{without}
doing any division.  Systematically try to circle numbers that are prime and 
cross out numbers that are not prime.  As a jesture of friendship, here are the numbers from $1$ to $120$.
\[
\begin{tabular}{r r r r r r r r r r}

  1 &   2 &   3 &   4 &   5 &   6 &   7 &   8 &   9 &  10\\
  \\
 11 &  12 &  13 &  14 &  15 &  16 &  17 &  18 &  19 &  20\\
 \\
 21 &  22 &  23 &  24 &  25 &  26 &  27 &  28 &  29 &  30\\
 \\
 31 &  32 &  33 &  34 &  35 &  36 &  37 &  38 &  39 &  40\\
 \\
 41 &  42 &  43 &  44 &  45 &  46 &  47 &  48 &  49 &  50\\
 \\
 51 &  52 &  53 &  54 &  55 &  56 &  57 &  58 &  59 &  60\\
 \\
 61 &  62 &  63 &  64 &  65 &  66 &  67 &  68 &  69 &  70\\
 \\
 71 &  72 &  73 &  74 &  75 &  76 &  77 &  78 &  79 &  80\\
 \\
 81 &  82 &  83 &  84 &  85 &  86 &  87 &  88 &  89 &  90\\
 \\
 91 &  92 &  93 &  94 &  95 &  96 &  97 &  98 &  99 & 100\\
 \\
101 & 102 & 103 & 104 & 105 & 106 & 107 & 108 & 109 & 110\\
\\
111 & 112 & 113 & 114 & 115 & 116 & 117 & 118 & 119 & 120\\
\end{tabular}
\]

Describe your method.  
\end{prob}

\begin{prob}
In the previous problem, after circling a new prime, what was the first number crossed out with that prime?  What was the biggest prime for which you crossed out at least one multiple?
\end{prob}


\begin{prob}
Find all of the prime factors of 1008. How can you be sure you've
found them all?
\end{prob}
